\LARGE \bf Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting

### 2014-12-10 main.tex
Removed a bit of passive voice + make other sentences simpler

%%% HRI 2015 -> double-blind review process

%Despite the social motivation for the use of a teachable agent for the
%engagement and support of children with handwriting difficulties, to date no
%such technology is known to have been developed.

%(DH) abstract probably too long...
%(DH) do we have to be specific somewhere about what stage of handwriting we're targeting..?

This article presents the first known robotic partner which children can teach handwriting. 
The system allows for the
\emph{learning by teaching} paradigm to be employed in the interaction, so as to
stimulate meta-cognition, empathy and increased self-esteem in the child user. 
It is
hypothesised that use of a humanoid robot in such a system could not just engage an unmotivated student,
but could also present the opportunity for children to experience physically-induced
benefits encountered during human-led handwriting interventions, such as motor
mimicry.

@@

Preliminary in situ studies have been conducted with primary school classes to obtain
insight into children's use of the novel system. 
Children aged 6-8 were successfully able to engage with the robot and to improve its 
writing to a level which they were satisfied with. The validation of the interaction
represents a significant step towards an innovative use for robotics which addresses a
widespread and socially meaningful challenge in education.

%, and provides context
%for robotics in education beyond the well-explored use of teaching coding and
%robotics-related subjects.

@@

The \emph{learning by teaching} paradigm, which engages the target student in
the act of teaching another, has been shown to produce motivational,
meta-cognitive, and educational benefits in a range of disciplines
\cite{Rohrbeck2003}. The application of the paradigm to handwriting intervention
is previously unexplored. One reason for this may due to the requirement of 
an appropriately unskilled peer for the target child to tutor, as this may present
a logistical constraint if the target child is the lowest performer in their class. 
In some cases, it may be appropriate for a
peer or teacher to simulate a na\"ive learner for the target child to teach.
For handwriting, where one's skill level is visually evident, however, 
this acting is likely to be eventually detected. As such,
there is motivation for the use of a teachable agent which can be configured for
a variety of skill levels, and for which children do not have preconceptions
about its handwriting ability.

We present the development of the first known teachable agent
that intentionally makes mistakes typical of children learning
handwriting. Through this capability, the robot can be taught by
children, who themselves may learn through their teaching.

Teachable computer-based agents have previously been used to encourage the 
``protégé effect'', wherein students invest more effort into learning when it
is for a teachable agent than for themselves \cite{Chase2009}. As we are 
concerned with learning of a physical skill, the learning agent developed has 
been embodied in a humanoid robot which is capable of physically demonstrating 
handwriting trajectories to its child learning partner.
This is supported by the potential for motor mimicry to yield significant 
improvements in handwriting interventions in which letter formations are 
demonstrated to participants \cite{Berninger1997}.

@@

%Indeed, as a commercially affordable robot is being used, the handwriting that
%it engages in is in fact emph{simulated}, for interaction purposes, by 
%leveraging synchronisation with a tablet display. Hence the system does not 
%have, nor does it depend on, capabilities to improve its physical skills for
%its own benefit.

@@

Within this article, Section \ref{sec:learningAlgorithm} presents the novel work in the area of
artificial intelligence to develop a learning algorithm suitable for a teachable
agent in the context of handwriting. Section \ref{sec:robotWriting} details the
extension of this algorithm to an embodied robotic learning agent, including the
new approach for achieving simulated fine motor skills on commercially
affordable humanoid robots. Section \ref{sec:experiment} explores the 
contributions made to the study of human-robot interaction, in discussing the
use of the first-of-its-kind system with primary school children and its potential as a tool for
addressing wider pedagogical research questions in education. Finally, Section \ref{sec:futureWork} addresses the challenges which are faced in extending this system to a level suitable for long-term studies, and Section \ref{sec:conclusions} concludes by reiterating the content and impact of the article's contributions.

@@

For the development of a learning algorithm in the context of
handwriting, a parameterisation of letters and their deformities has been sought such 
that different quality shapes can be generated, depending on the parameters input to
the letter models. This allows the system to be configured to improve its writing 
by modifying the parameters based on feedback from the 
reinforcement learning partner, as will be addressed in Section \ref{sec:learningAlg}. 
%To this end, a method which can generate a model from real-world data
%has been employed in order to capture realistic variations in letters.

@@

One approach for a shape model which can appropriately represent realistic
variations in shapes is statistical shape
modelling. Statistical shape modelling is an application of principle component
analysis (PCA), where a linear transform which de-correlates data vectors is
found \cite{Stegmann2002} and allows for dimensionality reduction.

@@

The projection from the original $2n$-dimensional feature space $(n=70)$ to a reduced
$N$-dimensional space is found as in (\ref{eq:projection}), where ${\bf p}$
contains the coordinates in the $N$-dimensional space with ${\bf 0}$-origin,
calculated as in (\ref{eq:paramCalc}). 
${\bf \Phi }$ is
an orthogonal $2n\times N$ matrix composed of the eigenvectors ${\bf v}_i$ corresponding to
the largest $N$ eigenvalues ($\lambda_i$) of the covariance matrix of the
observations, as shown in (\ref{eq:transformCalc}) \cite{Stegmann2002}. 
If there is correlation between the points in the observations, there will be
eigenvalues of the covariance matrix which are close to zero. As such, removing
the associated eigenvectors from ${\bf \Phi}$ allows for dimensionality
reduction with minimal impact.

@@

Interestingly, although the parameters are the result of an \emph{unsupervised} 
shape analysis, they still represent variations which could have
been intuitively identified by a manual parameterisation. For example, for the
model shown in Figure \ref{fig:deviations_sPrint}, the parameters may represent
the height of the top half of the letter compared to the bottom half, the width
of the overall shape, etc. The ability to create varied levels of deformations
which may be ascribed descriptive interpretations (not just numerical) is an
advantage of this method, given its intended use with humans. If a teacher wishes to
create initial letters with a particular feature (a wide `s' or a `d' with a
large loop, for example), it is possible.

@@

As aforementioned, new letters can be generated by varying the parameter values 
for a shape model in accordance with (\ref{eq:projection}). By choosing
parameter values which lie within the observed range in the dataset, it is
possible to produce letters which are more likely to be reasonable looking.
When the parameter values are outside of the range observed in the dataset, they
are less likely to represent shapes from the dataset of adult-written letters, 
and as a result are more likely to represent poor shapes.
Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
models of `e' and `g' by selecting random values for the first 5 parameters 
from a distribution with
standard deviation of $3\sqrt\lambda_i$ rather than the $\sqrt\lambda_i$
standard deviation observed in the dataset.

@@

%todo
In \cite{Chandra2013}, it was found that children aged 4-6 years participating
in a handwriting peer tutoring pilot study most often made mistakes classified
as inappropriate \emph{internal proportions} or \emph{global deformations}. It
would be reasonable to consider the shapes in Figure \ref{fig:sampleLetters} in
the same general categories. Using a database of children's letters when
available may yield potential for parameterising other mistakes made by
children, such as merging strokes or decomposing a shape into multiple subparts
inappropriately. Nevertheless, sufficient capabilities for the shape model to
generate `poor' letters which are appropriate for simulating a na\"ive learner
in the context of handwriting have been demonstrated, using the shape model
generated from PCA on a dataset of only adults' writing.

@@

The statistical shape model may be used to determine the parameters of a
demonstration shape by projecting the features of the observed shape into the
lower-dimensional space determined by the model. Mathematically, given a
demonstration ${\bf x}_{demo}$, the associated parameters may be determined as in
(\ref{eq:param}), which will reconstruct an approximate shape.

@@

In order to develop a teachable agent that is appropriate for engaging a child
in the learning by teaching paradigm, 
%- that is, that it is an embodied agent, capable of eliciting motor mimicry,
%and capable of causing its teacher to reflect on the process that has been used
%to respond to handwriting feedback -
capabilities for the robot to engage in handwriting and interactive turn-taking have been established.

@@

%Because of the challenges in getting the {\sc nao} to write trajectories smoothly
%because of its inherent ability to only reach discrete points in space, 
Precise control over what the robot is writing is necessary in the
proposed application of a handwriting. Because
of the limited fine motor skills possible with such an affordable robot, in
addition to the absence of force feedback and other technical necessities, the
{\sc nao} has been configured to use simulated handwriting with a synchronised tablet
to achieve this level of control.

@@

When using simulated handwriting, it is no longer necessary that the robot
engages in the typical style of handwriting of using a writing instrument at a desk.
By instead having the robot point at a vertical writing surface to cause the
trajectory to appear (as in Figure \ref{fig:naoWriting}), several advantages are
presented:

@@

    \item Perhaps most significantly, the accuracy of the matching of the
        robot's motion with the trajectory displayed on the tablet is not as
        critical. This is because a pen tip would be expected to touch the
        tablet exactly at the trajectory point, while a fingertip may not.
        % This means that orientation degrees of freedom can be freed without significant adverse effects.

@@

\begin{figure}[thpb]
     \begin{center}
        %\subfigure{
        %    \includegraphics[width=0.4\textwidth]{figures/naoWriting1.png}
        %}%
        \subfigure{
            \includegraphics[width=0.6\linewidth]{figures/naoWriting2.png}
        }%
%
    \end{center}
    \caption{A demonstration of the robot simulating the writing of a word with
    its finger. The motion of the robot is synchronised with the display of the
    tablet, communicating over ROS.\protect\footnotemark}%

@@

Therefore, the system presented utilises the context where the robot is
simulating handwriting by pointing at the tablet\footnote{Teachers interviewed
for their feedback on the system advised that children are asked to draw letters
in the air in a similar manner as part of their handwriting education. The behaviour 
is hence not unfamiliar to children.}. As
interacting with a tablet with one's finger is not uncommon, this may aid the
acceptance of the writing style by users.

@@

To enable the robot's `writing' to display while the robot is tracing
trajectories, ROS has been used for the communication between the devices,
including the Android tablet\footnote{For more information about ROS on Android
devices see \url{http://wiki.ros.org/android}}. As a result, aspects of the
networking between the tablet and the robot, such as the overheads associated
with connections, ports, message formats, etc. have been simplified.

@@

\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.35\textwidth]{figures/chilitagDetection_cameraOverlay.png}
    \caption{\label{fig:tabletDetection}Detection of the tablet using a fiducial
    marker to represent the origin of the writing surface frame, visualised in RViz. The robot's
    camera image is on the left, with the text trajectory overlay visible.}

@@

The fusion of the embodied handwriting agent developed with the handwriting
learning algorithm presented in Section \ref{sec:learningAlgorithm} involves the
integration of three components: the robot, the tablet, and a central controller
(Figure~\ref{fig:archi}). The robot and Android tablet application present the
writing process/result to the user, as in Section \ref{sec:tabletSynch}.
The tablet application has been extended to act as the primary medium for
capturing participant input, and submits the user's demonstrations when they are
satisfied with their writing.

The user demonstrations are received by the
interaction controller running on a desktop computer. It is responsible for
getting the {\sc nao} to prompt and respond appropriately to feedback received using
a finite state machine to manage the interaction stage and various system
inputs. In the context of learning handwriting, an additional input to the system 
is a word from which the letters are to be learned, which is detected by a fiducial 
marker on the card displaying the word.
The controller provides inputs to the learning algorithm including the word to learn
and the user demonstrations, by inferring the letter which the demonstrations are 
intended for based on their position on the tablet. The output shapes from the 
learning algorithm are sent by the controller to the devices which are to be write them.

@@

In addition to constituting a technically novel system, the presented teachable
robotic agent represents a tool which may be used for investigating social and
pedagogical research questions. For example, one such question is what impact the addition of
such a teachable robotic agent would have on the outcomes of a typical
handwriting intervention. 
Preliminary studies at two schools in the Geneva area, involving more than 50 children, 
have been conducted to evaluate the feasibility and technical soundness of the 
interaction system proposed as a tool for such investigations.

@@

    \item The robot asks for feedback from the participant and they demonstrate
        how to write the letter which they feel needs to be corrected. The
        tablet may be moved into the most appropriate position for the child to
        write on it with the stylus. Only one letter may be demonstrated at a time and the
        position of the participant's demonstration on the tablet encodes the
        letter that it is a demonstration for. The participant can remove and
        repeat their letter if they are unhappy with it.
        %, or if it is in the wrong position as determined by the researcher
        %conducting the interaction
        When the participant is satisfied with the demonstration, a button on
        the tablet which signals that it is the robot's turn is pressed.

@@

\subsection{Outcomes of Preliminary Study 2}
The study at the second school involved 21 french-speaking students aged 7-8 years. 7 children
interacted with the robot individually and 7 sessions included the remaining
14 students interacting with the robot in pairs.
Initial parameters were drawn from a range purposely chosen to generate shapes 
for letters 'e' and 's' which would elicit correction. For the other letters, 
parameters were fixed, generating shapes which some groups chose to correct 
(e.g. 13/14 for 'n' and 2/14 for 'c'). The duration of the sessions
was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3).

@@

Furthermore, no child indicated that they did not attribute the writing
to the robot. There were, at times, 
    questions about the robot's writing method at the beginning of the interaction,
    but when advised that the robot ``tells the tablet what it wants to write,''
    this was accepted by the children. 
%     To allow the children an opportunity to
%     express doubt in the robot's ability to write without explicitly asking them if
%     the robot was pretending, the children were asked if they believed that the
%     robot would be able to write its name, \emph{{\sc nao}} which had not previously been
%     demonstrated. It was reasoned that this would prompt the children to question
%     the point of the robot actually \emph{writing} if they had any suspicion that
%     the robot was pretending, but this was never the case. 
    On the rare occasion that the
    robot's writing was not correctly synchronised with the tablet, this did
    not appear to influence the children's impression. 
    If older children participate in the interaction study --
    which may be likely as children with lasting handwriting difficulties are included
    as participants -- it may become more important to invest time into the
    believability of the robot's writing scheme. However, for 6-8 year olds the
    proposed setup appears sufficient.

Regarding the engagement of the children in teaching the robot, 
    an average of 10.9 demonstration letters (SD = 4.4) were
    provided to the robot for each session during the interaction.
    In 9 out of the 14 sessions (64\%), the robot received demonstration letters
    \emph{after} reaching the test stage of the interaction. The participants'
    teaching after the test word had been written and evaluated -- the only
    purposefully imposed external motivation -- may suggest that by that time
    the participants had become intrinsically motivated to engage in the
    interaction.

@@

A conclusion drawn in a systematic review handwriting intervention studies \cite{Hoy2011} 
is that any of the studies considered which involved 
fewer than two practice sessions per week and fewer than a total of 20 practice 
sessions, including homework, were not found to demonstrate effective results. This 
highlights the necessity to engage students in an interaction which will be sustainable
 over the long-term if 
research questions which involve the measurement of learning gains are to be addressed. 
Several challenges are raised in developing such long-term capabilities for the system,
 from both technical and sociological points of view. %not sure this makes sense

@@

How the children's perception of the robot as a learning agent may change over the 
long-term remains to be seen. On one occasion during the preliminary studies, a 
child's response to whether or not the {\sc nao} could write its own name included that it 
may have problems with the `n', as the child had been correcting the robot on this 
letter. This suggests that users may project human-like learning features, such as 
forgetfulness, onto the robot, which may or may not actually be technically present 
in the learning agent. This may need to be capitalised on when considering how to 
extend the interaction for long time frames, as the present system -- with a learning rate 
such that progress is evident to the user -- will cause convergence for a letter within a 
few iterations.

@@

We believe that this article introduces three noteworthy contributions: an innovative
application of data processing and artificial intelligence for the
learning of hand-written letters suitable for educative purposes; a robotic
system which has been experimentally proven to provide convincing scaffolding for
complex human-robot interactions (teacher-learner social interactions, learning by
demonstration, simulated robotic fine motor skills); and an initial experimental investigation of what appears to be a
new role for robots in education.

@@

However, we believe that the strongest impact of this work is for the human-robot
interaction community and relates to the very \emph{nature} of the interaction
fostered by this research. The work presented here investigates a particular
role for a robot in the education of handwriting: not only is the robot actively
performing the activity by drawing letters, but it does so in a way that engages
the child in a very specific social role. The child is the teacher in this relationship and the robot is
the learner: the child must engage in a (meta-)cognitive relationship with the robot
to try to understand why the robot fails and how to help it best.  Here, the
robot is more than just an activity facilitator or orchestrator -- its physical presence
and embodiment induce agency and anthropomorphising, and cognitively engage the
child into the learning activity, which we predict will lead to higher learning
efficacy.

@@

The strong social impact of early educational problems makes continued research in this field
an undoubtably meaningful challenge for robotics and human-robot interaction.

>>>>

This article presents a novel robotic partner which children can teach
handwriting.  The system relies on the \emph{learning by teaching} paradigm to
build an interaction, so as to stimulate meta-cognition, empathy and
increased self-esteem in the child user.  We hypothesise that use of a
humanoid robot in such a system could not just engage an unmotivated student,
but could also present the opportunity for children to experience
physically-induced benefits encountered during human-led handwriting
interventions, such as motor mimicry.

@@

Preliminary in situ studies have been conducted with primary school classes to
obtain insight into children's use of the novel system.  Children aged 6-8
successfully engaged with the robot and improved its writing to a level which
they were satisfied with. The validation of the interaction represents a
significant step towards an innovative use for robotics which addresses a
widespread and socially meaningful challenge in education.

@@

The \emph{learning by teaching} paradigm, which engages the target student in
the act of teaching another, has been shown to produce motivational,
meta-cognitive, and educational benefits in a range of disciplines
\cite{Rohrbeck2003}. To our best knowledge, the application of the paradigm to
handwriting intervention remains however unexplored. One reason for this may due
to the requirement of an appropriately unskilled peer for the target child to
tutor, as this may present a logistical constraint if the target child is the
lowest performer in their class.  In some cases, it may be appropriate for a
peer or teacher to simulate a na\"ive learner for the target child to teach.
For handwriting, where one's skill level is visually evident, however, this
acting is likely to be eventually detected. As such, there is motivation for the
use of a teachable agent which can be configured for a variety of skill levels,
and for which children do not have preconceptions about its handwriting ability.

We present the development of a novel teachable agent
that intentionally makes mistakes typical of children learning
handwriting. Through this capability, the robot can be taught by
children, who themselves may learn through their teaching.

Teachable computer-based agents have previously been used to encourage the 
``protégé effect'', wherein students invest more effort into learning when it
is for a teachable agent than for themselves~\cite{Chase2009}. As we are 
concerned with learning of a physical skill, the learning agent developed has 
been embodied in a humanoid robot which is capable of physically demonstrating 
handwriting trajectories to its child learning partner.
This is supported by the potential for motor mimicry to yield significant 
improvements in handwriting interventions in which letter formations are 
demonstrated to participants~\cite{Berninger1997}.

@@

@@

Within this article, Section \ref{sec:learningAlgorithm} presents the novel work in the area of
artificial intelligence to develop a learning algorithm suitable for a teachable
agent in the context of handwriting. Section \ref{sec:robotWriting} details the
extension of this algorithm to an embodied robotic learning agent, including the
new approach for achieving simulated fine motor skills on commercially
affordable humanoid robots. Section \ref{sec:experiment} explores the 
contributions made to the study of human-robot interaction, in discussing the
use of the system with primary school children and its potential as a tool for
addressing wider pedagogical research questions in education. Finally, Section \ref{sec:futureWork} addresses the challenges which are faced in extending this system to a level suitable for long-term studies, and Section \ref{sec:conclusions} concludes by reiterating the content and impact of the article's contributions.

@@

For the development of a learning algorithm in the context of
handwriting, a parameterisation of letters and their deformities has been sought such 
that different quality shapes can be generated, depending on the parameters input to
the letter models. This allows to configure the system such as to improve its writing 
by modifying the parameters based on feedback from the 
reinforcement learning partner (Section~\ref{sec:learningAlg}).

@@

We use statistical shape modelling as an approach for a shape model which can
appropriately represent realistic variations in shapes. Statistical shape
modelling is an application of principle component analysis (PCA), where a
linear transform which de-correlates data vectors is found~\cite{Stegmann2002}
and allows for dimensionality reduction.

@@

Equation (\ref{eq:projection}) represents the projection from the original 
$2n$-dimensional feature space $(n=70)$ to a reduced $N$-dimensional space, where ${\bf p}$
contains the coordinates in the $N$-dimensional space with ${\bf 0}$-origin,
calculated as in (\ref{eq:paramCalc}). 
${\bf \Phi }$ is
an orthogonal $2n\times N$ matrix composed of the eigenvectors ${\bf v}_i$ corresponding to
the largest $N$ eigenvalues ($\lambda_i$) of the covariance matrix of the
observations, as shown in (\ref{eq:transformCalc}) \cite{Stegmann2002}. 
If there is correlation between the points in the observations, there will be
eigenvalues of the covariance matrix which are close to zero. As such, removing
the associated eigenvectors from ${\bf \Phi}$ allows for dimensionality
reduction with minimal impact.

@@

Interestingly, although the parameters are the result of an \emph{unsupervised} 
shape analysis, they still represent variations which could have
been intuitively identified by a manual parameterisation. For example, for the
model shown in Figure \ref{fig:deviations_sPrint}, the parameters may represent
the height of the top half of the letter compared to the bottom half, the width
of the overall shape, etc. The ability to generate varied levels of deformations
which may be ascribed descriptive interpretations (not just numerical) is an
advantage of this method, given its intended use with humans: It is for instance
possible for a teacher to create initial letters with a particular feature (a wide
`s' or a `d' with a large loop, for example).

@@

As explained, new letters can be generated by varying the parameter values 
for a shape model in accordance with (\ref{eq:projection}). By choosing
parameter values which lie within the observed range in the dataset, it is
possible to produce letters which are more likely to be reasonable looking.
When the parameter values are outside of the range observed in the dataset, they
are less likely to represent shapes from the dataset of adult-written letters, 
and as a result are more likely to represent poor shapes.
Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
models of `e' and `g' by selecting random values for the first 5 parameters 
from a distribution with
standard deviation of $3\sqrt\lambda_i$ rather than the $\sqrt\lambda_i$
standard deviation observed in the dataset.

@@

%todo
In~\cite{Chandra2013}, it was found that children aged 4-6 years participating
in a handwriting peer tutoring pilot study most often made mistakes classified
as inappropriate \emph{internal proportions} or \emph{global deformations}. It
would be reasonable to consider the shapes in Figure \ref{fig:sampleLetters} in
the same general categories.

Using a database of children's letters when
available may yield potential for parameterising other mistakes made by
children, such as merging strokes or decomposing a shape into multiple subparts
inappropriately. Nevertheless, our current shape model
generated from PCA on a dataset of only adults' writing has shown to be
initial well-suited to generate `poor' letters which are appropriate for 
simulating a na\"ive learner.

@@

The statistical shape model is used to determine the parameters of a
demonstration shape by projecting the features of the observed shape into the
lower-dimensional space determined by the model. Mathematically, given a
demonstration ${\bf x}_{demo}$, the associated parameters may be determined as in
(\ref{eq:param}), which will reconstruct an approximate shape.

@@

In order to develop a teachable agent that is appropriate for engaging a child
in the learning by teaching paradigm, we have established capabilities for the robot 
to engage in handwriting and interactive turn-taking.

@@

Precise control over what the robot is writing is necessary in the
proposed application of a handwriting. Because
of the limited fine motor skills possible with such an affordable robot, in
addition to the absence of force feedback and other technical necessities, we
have configured the {\sc nao} to use simulated handwriting with a synchronised tablet
to achieve this level of control.

@@

When using simulated handwriting, it is no longer necessary that the robot
engages in the typical style of handwriting of using a writing instrument at a desk.
Having the robot point at a vertical writing surface to cause the
trajectory to appear (as in Figure \ref{fig:naoWriting}) has several
advantages:

@@

    \item Perhaps most significantly, the accuracy of the matching of the
        robot's motion with the trajectory displayed on the tablet is not as
        critical. This is because a pen tip would be expected to touch the
        tablet exactly at the trajectory point, while a fingertip may not.

@@

\begin{figure}[thpb]
     \begin{center}
            \includegraphics[width=0.7\linewidth]{figures/naoWriting2.png}
    \end{center}
    \caption{A demonstration of the robot simulating the writing of a word with
    its finger. The motion of the robot is synchronised with the display of the
    tablet, communicating over ROS.\protect\footnotemark}%

@@

We have therefore designed the system in such a way that the robot is
simulating handwriting by pointing at the tablet\footnote{Teachers interviewed
for their feedback on the system advised that children are asked to draw letters
in the air in a similar manner as part of their handwriting education. The behaviour 
is hence not unfamiliar to children.}. As
interacting with a tablet with one's finger is not uncommon, this may aid the
acceptance of the writing style by users.

@@

To enable the robot's `writing' to display while the robot is tracing
trajectories, ROS is used for the communication between the devices,
including the Android tablet\footnote{For more information about ROS on Android
devices see \url{http://wiki.ros.org/android}}. As a result, aspects of the
networking between the tablet and the robot, such as the overheads associated
with connections, ports, message formats, etc. have been simplified.

@@

\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.9\columnwidth]{figures/chilitagDetection_cameraOverlay.png}
    \caption{\label{fig:tabletDetection}Detection of the tablet using a fiducial
    marker to represent the origin of the writing surface frame, visualised in RViz. The robot's
    camera image is on the left, with the text trajectory overlay visible.}

@@

The fusion of the embodied handwriting agent developed with the handwriting
learning algorithm presented in Section \ref{sec:learningAlgorithm} involves the
integration of three components: the robot, the tablet, and a central controller
(Figure~\ref{fig:archi}). The robot and Android tablet application present the
writing process/result to the user, as explained in the previous section.
The tablet application has been extended to act as the primary medium for
capturing participant input, and submits the user's demonstrations when they are
satisfied with their writing.

The user demonstrations are received by the
interaction controller running on a desktop computer. It is responsible for
getting the {\sc nao} to prompt and respond appropriately to feedback received using
a finite state machine to manage the interaction stage and various system
inputs. In the context of learning handwriting, an additional input to the system 
is a word from which the letters are to be learned, which is detected by a fiducial 
marker on the card displaying the word.
The controller provides inputs to the learning algorithm including the word to learn
and the user demonstrations, by inferring the letter which the demonstrations are 
intended for based on their position on the tablet. The output shapes from the 
learning algorithm are sent by the controller to the devices which write them.

@@

In addition to constituting a technically novel system, the presented teachable
robotic agent represents a tool which may be used for investigating social and
pedagogical research questions. For example, one such question is what impact the addition of
such a teachable robotic agent would have on the outcomes of a typical
handwriting intervention. 
Preliminary studies at two schools in the Geneva area, involving above 50 children, 
have been conducted to evaluate the feasibility and technical soundness of the 
interaction system proposed as a tool for such investigations.

@@

    \item The robot asks for feedback from the participant and they demonstrate
        how to write the letter which they feel needs to be corrected. The
        tablet may be moved into the most appropriate position for the child to
        write on it with the stylus. Only one letter may be demonstrated at a time and the
        position of the participant's demonstration on the tablet encodes the
        letter that it is a demonstration for. The participant can remove and
        repeat their letter if they are unhappy with it.
        %, or if it is in the wrong position as determined by the researcher
        %conducting the interaction
        When the participant is satisfied with the demonstration, they press a button on
        the tablet which signals that it is the robot's turn.

@@

\subsection{Outcomes of Preliminary Study 2}
The study at the second school involved 21 french-speaking students aged 7-8 years. 7 children
interacted with the robot individually and 7 sessions included the remaining
14 students interacting with the robot in pairs.
Initial parameters were drawn from a range purposely chosen to generate shapes 
for letters 'e' and 's' which would elicit correction. For the other letters, 
parameters were fixed, generating shapes which some groups still chose to correct 
(e.g. 13/14 for 'n' and 2/14 for 'c'). The duration of the sessions
was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3).

@@

Furthermore, no child indicated that they did not believe that the robot was writing
by itself. There were, at times, 
    questions about the robot's writing method at the beginning of the interaction,
    but when advised that the robot ``tells the tablet what it wants to write,''
    this was accepted by the children. 
%     To allow the children an opportunity to
%     express doubt in the robot's ability to write without explicitly asking them if
%     the robot was pretending, the children were asked if they believed that the
%     robot would be able to write its name, \emph{{\sc nao}} which had not previously been
%     demonstrated. It was reasoned that this would prompt the children to question
%     the point of the robot actually \emph{writing} if they had any suspicion that
%     the robot was pretending, but this was never the case. 
    On the rare occasion that the
    robot's writing was not correctly synchronised with the tablet, this did
    not appear to influence the children's impression. 
    If older children participate in the interaction study --
    which may be likely as children with lasting handwriting difficulties are included
    as participants -- it may become more important to invest time into the
    believability of the robot's writing scheme. However, for 6-8 year olds the
    proposed setup appears sufficient.

Regarding the engagement of the children in teaching the robot, 
    an average of 10.9 demonstration letters (SD = 4.4) were
    provided to the robot for each session during the interaction.
    In 9 out of the 14 sessions (64\%), the robot received demonstration letters
    even \emph{after} reaching the test stage of the interaction. The participants'
    teaching after the test word had been written and evaluated -- the only
    purposefully imposed external motivation -- may suggest that by that time
    the participants had become intrinsically motivated to engage in the
    interaction.

@@

A conclusion drawn in a systematic review of handwriting intervention studies~\cite{Hoy2011} 
is that any of the studies considered which involved 
fewer than two practice sessions per week and fewer than a total of 20 practice 
sessions, including homework, were not found to demonstrate effective results. This 
highlights the necessity to engage students in an interaction which will be sustainable
 over the long-term if 
we want to address research questions which involve the measurement of learning gains. 
Several challenges are raised in developing such long-term capabilities for the system,
 from both technical and sociological points of view. %not sure this makes sense

@@

How the children's perception of the robot as a learning agent may change over the 
long-term remains to be seen. On one occasion during the preliminary studies, a 
child's response to whether or not the {\sc nao} could write its own name included that it 
may have problems with the `n', as the child had been correcting the robot on this 
letter. This suggests that users may project human-like learning features, such as 
forgetfulness, onto the robot, which can be implemented 
in the learning agent. This may need to be capitalised on when considering how to 
extend the interaction for long time frames, as the present system -- with a learning rate 
such that progress is evident to the user -- will cause convergence for a letter within a 
few iterations.

@@

We believe that this article introduces three noteworthy contributions: an innovative
application of data processing and artificial intelligence for the
learning of hand-written letters suitable for educative purposes; a robotic
system which has been experimentally shown to provide convincing scaffolding for
complex human-robot interactions (teacher-learner social interactions, learning by
demonstration, simulated robotic fine motor skills); and an initial experimental investigation of what appears to be a
new role for robots in education.

@@

However, we believe that the strongest impact of this work is for the human-robot
interaction community and relates to the very \emph{nature} of the interaction
fostered by this research. The work presented here investigates a particular
role for a robot in the education of handwriting: not only is the robot actively
performing the activity by drawing letters, but it does so in a way that engages
the child in a very specific social role. The child is the teacher in this relationship and the robot is
the learner: the child must engage in a (meta-) cognitive relationship with the robot
to try to understand why the robot fails and how to help it best.  Here, the
robot is more than just an activity facilitator or orchestrator -- its physical presence
and embodiment induce agency and anthropomorphising, and cognitively engage the
child into the learning activity, which we predict will lead to higher learning
efficacy.

@@

And the strong social impact of early educational problems makes continued research in this field
an undoubtedly meaningful challenge for robotics and human-robot interaction.
